---
title: "Untitled"
author: "Batuhan SAYLAM"
date: '2022-06-22'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(magrittr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(readr)
Fatalities <- read_csv("C:/Users/ASUS/Desktop/250 final/Fatalities.csv")
Fatalities=na.omit(Fatalities)
```


Simple lineer regression:

```{r}
model=lm(nfatal2124~afatal,data=Fatalities)
plot1=Fatalities %>% 
ggplot(aes(x = afatal, y = nfatal)) +
  geom_point(color="blue")+coord_cartesian(xlim=c(min(Fatalities$afatal),max(Fatalities$afatal)),ylim=c(min(Fatalities$nfatal),max(Fatalities$nfatal))) + geom_smooth(method = "lm", col = "green" )
plot1+theme_classic()
```

```{r}
print(summary(model))
```
Two sample test:
H0: the mean of afatal which breath is yes is equal to the mean of afatal which breath test is no

H1: the mean of afatal which breath is yes is not  equal to the mean of afatal which breath test is no
```{r}
breathy <- filter(Fatalities, Fatalities$breath == 'yes') 
breathno <- filter(Fatalities, Fatalities$breath == 'no')
ggplot(Fatalities, aes(Fatalities$afatal)) + 
geom_density(aes(data = Fatalities$afatal, fill = Fatalities$breath),   position = 'identity', alpha = 0.5) +
labs(x = 'death w/alchol', y = 'Density') + scale_fill_discrete(name = 'Breath') + theme_classic()

```




```{r}
breathy <- filter(Fatalities, Fatalities$breath == 'yes') 
breathno <- filter(Fatalities, Fatalities$breath == 'no')
test <- t.test(breathy[,"afatal"], breathno[,"afatal"])
test
```


From the output of the test we can see the p-value is equal to 0.001903, which is much less than 0.05. Therefore, we reject H0 and conclude there is a difference between the mean death wtih alchol of the breath test and no breath test.

One sample test:
H0:mean of drinkage=21
H1:mean of drinkage !=21
```{r}
test2=t.test(Fatalities$drinkage, mu=21)
test2
```

From the output of the test we can see the p-value is less than  2.2e-16, which is much less than 0.05. Therefore, we reject H0 and conclude the mean of drinkage is not equal to 21.



